---
title: "Analysis of scRNA-seq data from glioblastoma (GBM) patients with scBubbletree"
author: "Simo Kitanovski (simo.kitanovski@uni-due.de)"
output:
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
  pdf_document:
    toc: yes
    toc_depth: 2
vignette: "%\\VignetteIndexEntry{Analysis of scRNA-seq data from glioblastoma (GBM) patients with scBubbletree} %\\VignetteEncoding{UTF-8} %\\VignetteEngine{knitr::rmarkdown}\n"
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include = FALSE, warning = FALSE}
library(BiocStyle)
knitr::opts_chunk$set(comment = FALSE, warning = FALSE, message = FALSE,
                      collapse = TRUE, fig.align = "center")
```

# Background

Here we will use `r Biocpkg("scBubbletree")` to analyze scRNA-seq data
with over 45,000 cells from five human glioblastoma (GBM) patients[^1].
From each patient, we have paired samples from three tissues: tumor
center, peripheral infiltration zone, and blood. This vignette aims to
demonstrate that `r Biocpkg("scBubbletree")` can evaluate complex
scRNA-seq data from solid tumors. In our analysis, we compare our
results with those presented by Schmassmann et al., 2023, and highlight
the advantages of using `r Biocpkg("scBubbletree")`.

[^1]: Schmassmann et al., 2023 <https://doi.org/10.7554/eLife.92678.2>

# Data

The publicly available scRNA-seq data[^2] has been generated by 10X
Genomics Chromium Single Cell Controller. The raw data (barcode-gene
count matrix) is accompanied by supplementary meta-data. The metadata
includes the following cell-specific features:

[^2]: <https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE197543>

-   cell type labels (coarse- and fine-grained)
-   cell phase labels
-   sample name
-   tissue site
-   quality metrics: % of transcripts from mitochondrial/ribosomal genes

# Data processing

Data processing was performed with the R-package `r CRANpkg("Seurat")`.
Gene expressions were normalized (function `NormalizeData`),
highly-variable genes were identified (function `FindVariableFeatures`),
and the expressions were scaled and centered gene-wise (function
`ScaleData`). Next, principal component analysis (PCA) was performed
with the function `RunPCA` based on the 5,000 most variable genes.

In the data, we saw that the first 15 principal components capture most
of the variance in the data (data not shown), and the proportion of
variance explained by each subsequent principal component was
negligible. Thus, we used the single-cell projections (embeddings) in
15-dimensional feature space, $A^{45,466 \times 15}$.

```{r}
# # Description: we used this script to download the raw data and process it
# # as explained in the above paragraph .This script can be used to generate 
# # the data GBM data
# 
# # create directory
# dir.create(path = "case_study/")
# 
# # download the data from:
# https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE197543
#
# extract data: 
# gzip -d GSE197543_UMIsMatrix.txt.gz
# gzip -d GSE197543_colData.txt.gz
# 
# # read.csv
# u <- read.csv(file = "case_study/GSE197543_UMIsMatrix.txt", sep = "\t")
# 
# # create Seurat object from the raw counts and append the meta data to it
# d <- Seurat::CreateSeuratObject(counts = u, project = 'GBM')
# 
# # get meta
# meta <- read.csv(file = "data/CS_Glio/GSE197543_colData.txt", sep = "\t")
# meta_tissue <- do.call(rbind, strsplit(x = rownames(d@meta.data), split= "_"))
# d@meta.data <- cbind(d@meta.data, meta)
# d@meta.data$tissue <- meta_tissue[,4]
# d@meta.data$patient <- meta_tissue[,3]
# d@meta.data$cell_id <- 1:nrow(d@meta.data)
# 
# # normalize data
# d <- NormalizeData(object = d, normalization.method = "LogNormalize")
# 
# d <- FindVariableFeatures(object = d, selection.method="vst", nfeatures=5000)
# 
# d <- ScaleData(object = d, features = VariableFeatures(object = d))
# 
# d <- RunPCA(object = d, npcs = 50, features = VariableFeatures(object = d))
# 
# # Save file to new folder
# save(d, file = "case_study/d.RData")
# # matrix A: the main input of scBubbletree
# GBM_A <- d@reductions$pca@cell.embeddings[, 1:15]
# 
# save(A, file = "GBM_data/GBM_A.RData")
# save(d@meta.data, file = "GBM_data/GBM_meta.RData")
```

To run this vignette we need to load a few packages:

```{r}
library(scBubbletree)
library(ggplot2)
library(ggtree)
library(patchwork)
```

But first, load the PCA matrix, meta-data, and the matrix with
normalized gene expressions:

```{r}
# Load the data
# pca
load("GBM_data/GBM_A.RData")
# meta
load("GBM_data/GBM_meta.RData")
# gene expressions
load("GBM_data/GBM_exp.RData")
```

```{r, include=FALSE}
data_r <- get(load(file = "GBM_data/data_r.RData"))
```

# **Step 1:** determining the clustering resolution $r$ for Louvain clustering

One important objective in scRNA-seq data analysis is to identify groups
(clusters) of transcriptionally similar cells by clustering.
`r Biocpkg("scBubbletree")` offers several clustering methods (Louvain,
Leiden, k-means, etc.), most of which are also implemented in
`r CRANpkg("Seurat")`. Here we will use the original Louvain method.

To do clustering we need two sets of inputs:

1.  the PCA matrix
2.  clustering resolution $r$

### How to determine $r$? {.unlisted .unnumbered}

To determine the clustering resolution, we computed the gap statistic
for the Louvain method with resolution parameter $r=10^R$, where $R$ was
initialized using a sequence of values from -4 to 1 in steps of 0.1. At
each resolution we recorded the number $k'$ of identified communities.

```{r}
rs <- 10^seq(from = -4, to = 1, by = 0.1)
```

Next, we run the function `get_r`:

```{r, eval = F}
data_r <- get_r(B_gap = 20, cores = 20, rs = rs, 
                x = GBM_A, algorithm = "original")
save(data_r, file = "GBM_data/data_r.RData")
```

### How does the gap curve behave as a function of $r$? {.unlisted .unnumbered}

The gap increased rapidly between $k'=1$ and $k'=13$, followed by a dip
at $k'=14$ to a value below 4. Between $k'=13$ and $k'=25$, the gap
increased gradually by only about 0.15, even though 12 communities
(about two-fold more) were added in this interval. This suggested that
there is little benefit in using values of $r$ larger than 0.158
($k'=13$). At higher $k'$ we observed a slower and approximately linear
increase in the gap.

The value of $k'=13$ is close to the number of clusters identified in
the publication by Schmassmann et al., 2023, which reports between $k=10$
and $k=22$ clusters of transcriptionally similar cells. 


> Clustering of cells was performed with hierarchical clustering on the
> Euclidean distances between cells (with Ward's criterion to minimize
> the total variance within each cluster Murtagh and Legendre, 2014;
> package cluster version 2.1.0). The number of clusters used for
> following analyses was identified by applying a dynamic tree cut
> (package dynamicTreeCut, version 1.63--1) (Langfelder et al., 2008),
> resulting in 10 with argument deepSplit set to 1, or 22 clusters with
> argument deepSplit set to 2.


To find e.g. rare tumor cells, one can increase the resolution to e.g. 
$r=0.79$ ($k'=25$) or $r=2.51$ ($k'=45$). Note, that scBubbletree's 
clustering workflow is transparent. It demands from the user to think 
and evaluate different clustering resolutions and thereby understand 
the data. The only cost is the additional computational time required 
to run `get_r` or `get_k`.

```{r, fig.width=7, fig.height=3}
g1 <- ggplot(data_r$gap_stats_summary)+
   geom_line(aes(y = gap_mean, x = k), col = "darkgray")+
   geom_point(aes(y = gap_mean, x = k), size = 1, col = "black")+
   geom_errorbar(aes(y = gap_mean, x = k, ymin = L95, ymax = H95), width = 0.1)+
   xlab(label = "k'")+
   ylab(label = "Gap")+
   theme_bw(base_size = 10)

g2 <- ggplot(data_r$gap_stats_summary)+
    geom_point(aes(x = k, y = r), size = 1, col = "black")+
    ylab(label = "r")+
    xlab(label = "k'")+
    scale_x_log10()+
    scale_y_log10()+
    annotation_logticks(base = 10, sides = "lb")+
    theme_bw(base_size = 10)


g1|g2+plot_annotation(tag_levels = 'A')
```



# **Step 2-3:** clustering and hierarchical bubble grouping $\rightarrow$ bubbletree

For clustering of dataset GBM we will use the original Louvain method and 
a resolution parameter $r=0.158$ ($k'=13$). First, we will construct an 
SNN graph based on $A^{45,466 \times 15}$, where each vertex (cell) in 
the SNN graph is connected to its 50 nearest neighbors. Clustering will 
be performed with 20 random starts and up to 100 iterations in each run.
The clusters will be organized in a bubbletree using hierarchical clustering 
with average linkage. For this we will use $B=1,000$ bootstrap iterations 
and draw samples with up to $N_\textit{eff}=100$ cells from each cluster 
to compute inter-cluster distances:

```{r}
# graph-based clustering -> bubbletree
btd <- get_bubbletree_graph(x = GBM_A,
                            r = 0.158,
                            algorithm = "original",
                            hclust_method = "average",
                            hclust_distance = "euclidean",
                            cores = 5,
                            B = 1000,
                            show_simple_count = TRUE,
                            N_eff = 100)
```


# **Step 4:** bubbletree visualization and annotation

## Lets inspect the bubbletree

```{r, fig.width=5, fig.height=3}
btd$tree
```

The resulting bubbletree has 13 bubbles with sizes ranging from about
11,800 cells (26%, cluster 0) down to 184 cells (0.4%, cluster 12).
Nearly all branches in the bubbletree are completely robust. The branch
between bubbles 2 and 3 has low branch support as it is found in only
457 out of 1,000 bootstrap dendrograms.


## Annotating the bubbletree with cell features

For biological interpretation of the bubbletree structure, we will
annotate the bubbletree with cluster-specific summaries of different
cell features. Here, we will use the function `get_cat_tiles` to
generate heatmaps for each of the following categorical features, which
are provided as part of the meta-data:

1.  coarse-grained cell type labels
2.  fine-grained cell type labels
3.  cell phases
4.  sample labels

We will use the input parameter `integrate_vertical = FALSE`. This means
that we will show the composition of each bubble (y-axis) with respect
to the categories (labels; x-axis) of each feature, i.e. the
within-bubble relative frequency of the different labels.

To visualize numeric features, such as mean gene expressions in each
bubble, we will use the functions `get_num_tiles`, `get_num_violins`,
and `get_num_cell_tiles`.


## What is the **cell type** composition of the bubbles?

To determine which cell types are enriched in each bubble, we will visualize
the within-bubble relative frequencies of fine- and coarse-grained cell
type labels (heatmaps in Figs. B and C, below). To this end, we will run
the function `get_cat_tiles` using as input two categorical features
(two columns in `GBM_meta`: CellAnnotation and CellAnnotationFine),
which provide the predicted cell type labels of each cell at two levels
of resolution: coarse- grained and fine-grained, respectively.

```{r, fig.width=8.5, fig.height=5}
# cell type annotations
g_c <- get_cat_tiles(btd = btd,
                     f = GBM_meta$CellAnnotation,
                     round_digits = 1,
                     tile_text_size = 2,
                     integrate_vertical = FALSE)

# cell type 'fine' annotations 
g_cf <- get_cat_tiles(btd = btd,
                      f = GBM_meta$CellAnnotationFine,
                      round_digits = 1,
                      tile_text_size = 2,
                      integrate_vertical = FALSE)

g_ct <- (btd$tree|g_c$plot|g_cf$plot)+
  plot_layout(widths = c(1, 1, 1.5))+
  plot_annotation(tag_levels = 'A')

g_ct
```

The analysis shows that more than 95% of the cells in bubbles 8, 5, 11,
10, and 12 were CD45- (non-hematopoietic cells), while the remaining
bubbles are enriched with immune cells, consistent with the results
reported in Schmassmann et al., 2023.

The bubbletree conserves global transcriptional distances between
bubbles, grouping them into a PBMC clade with T-cells (bubbles 3, 2, and
1), B-cells (bubble 7), NK-cells (bubbles 3 and 2), monocytes (bubbles
9, 0, and 4), and neutrophils (bubbles 9 and 4). Additionally, it
identifies multiple non-PBMC populations including microglia (bubble 6),
macrophages (bubble 4), tumor cells (bubbles 5 and 8), and other smaller
cell populations.


## What is the **tissue** composition of the bubbles?

Dataset GBM contains samples from three tissues: PBMC, tumor center, and
peripheral infiltration zone. Using tissue as categorical cell features,
we will next visualize the relative frequency of cells from a specific tissue
within the different bubbles (heatmap in Fig. D).

```{r, fig.width=9.5, fig.height=5}
# tissue
g_t <- get_cat_tiles(btd = btd,
                     f = GBM_meta$tissue,
                     round_digits = 1,
                     tile_text_size = 2,
                     integrate_vertical = FALSE)

g3 <- (g_ct|g_t$plot)+
  plot_layout(widths = c(1, 1, 1.5, 0.4))+
  plot_annotation(tag_levels = 'A')

g3
```

We observe that many bubbles enriched with PBMC cell types had high
relative frequency of cells from PBMC tissue, except for bubble 3, which
contains a mixture of cells from the tumor center and peripheral
infiltration zone tissues. Hence, bubble 3 may contain
tumor-infiltrating lymphocytes. The remaining bubbles in the bubbletree
contain a mixture of cells from tumor center and peripheral
infiltration zone tissues. Meanwhile, bubbles 5 and 8 are mostly
composed of tumor cells from tumor centers.

### Lets compare the previous visual with a 2D t-SNE plot {.unlisted .unnumbered}

We will plot the same 2D t-SNE visual reported by Schmassmann et al.,
2023.

```{r, fig.width=7, fig.height=3.25}
g4 <- ggplot(data = GBM_meta)+
  facet_wrap(facets = ~tissue, nrow = 1)+
  geom_point(aes(x = tSNE1, y = tSNE2, col = CellAnnotation), size = 0.25)+
  theme_bw()+
  theme(legend.position = "top")+
  guides(colour = guide_legend(override.aes = list(size=2)))+
  scale_color_discrete(name = "tissue")

g4
```

Global distances between the clusters are **not** adequately conserved
in the 2D t-SNE plot. Furthermore, the 2D t-SNE plot suffers from heavy
overplotting, despite the fact that the cells are split into three
panels for each tissue site.

## Compositional analysis: are cells from different samples **evenly mixed** within bubbles?

Dataset GBM contains samples from five patients and three tissues. Using
tissue and patient as categorical cell features, we will visualize the
relative frequency of cells from a specific tissue and patient across
the different bubbles (heatmap in Fig. B, below) as well as within the
bubbles (heatmap in Fig. C, below). This allows us to check for
compositional biases, which is essential to e.g. identify novel cell
types (e.g. tumor cells), or to detect systematic biases (e.g. batch
effects) in a subset of the samples.

```{r, fig.width=9.5, fig.height=5.25}
g_p_v <- get_cat_tiles(btd = btd,
                     f = paste0(GBM_meta$tissue, '-', GBM_meta$patient),
                     round_digits = 1,
                     tile_text_size = 2,
                     integrate_vertical = TRUE)

g_p_h <- get_cat_tiles(btd = btd,
                     f = paste0(GBM_meta$tissue, '-', GBM_meta$patient),
                     round_digits = 1,
                     tile_text_size = 2,
                     integrate_vertical = FALSE)

g5 <- (btd$tree|g_p_v$plot|g_p_h$plot)+
    plot_layout(widths = c(1, 1.3, 1.3))+
    plot_annotation(tag_levels = 'A')

g5
```

In the next, we describe the key compositional biases:

-   First, all PBMC samples (middle columns in Fig. B, above) have
    similar relative abundances across the bubbles. In contrast, the
    samples from tumor center and peripheral infiltration zone are
    heterogeneous in terms of their relative abundances across the
    bubbles.

-   Second, all bubble 5 cells come from patient 604 (95.6% from
    center-604 and 4.4% periphery-604) (Fig C, above), and 69.4% of the
    cells in sample center-604 are assigned to bubble 5 (NPC-like tumor
    cells)

-   Third, the majority of cells in bubbles 11, 10, and 12 came from
    patients 604 and 617.


In summary, we observed high degree of GBM heterogeneity between individuals. 
Yet, despite these biases, from Schmassmann et al., 2023, we get the following 
remarks about the degree of overlap of cells from the different patients 
across cell types (clusters):

> As we observed a good overlap of cells across patients for most of the
> dataset (see Methods; Figure 1-figure supplement 2B-F), we chose not
> to perform any correction for patient-specific effects

> A quantitative test of overlap of cells across patients was made using
> the CellMixS package (Lütge et al., 2021) (version 1.12.0) developed
> to quantify the effectiveness of batch correction methods. We used the
> cell-specific mixing (CMS) score, which highlighted a very good
> overlap across cells from different patients in the lymphoid
> compartment and for the monocytes. The myeloid compartment displayed a
> slightly elevated patient- specific structure, while it was most
> pronounced for the CD45 negative subset.


## **Quality control** with `r Biocpkg("scBubbletree")`

Finally, nearly every scRNA-seq data analysis begins with quality
control (QC). scBubbletree allows you to explore QC metrics commonly
used by the community:

1.  the number of unique genes detected in each cell
2.  total number of molecules detected within a cell
3.  the percentage of reads that map to the mitochondrial genome

Furthermore, any cell feature (numeric or categorical) that can be used
for QC. These can be attached to the bubbletree to identify bubbles
enriched with low-quality cells.

```{r}
g_qc <- get_num_violins(btd = btd,
                        f = as.matrix(GBM_meta[, c("PercentMitochondrial",
                                                   "PercentRibosomal",
                                                   "NumberDetectedGenes")]))
```

```{r, fig.width=8, fig.height=5}
(btd$tree|g_qc$plot)+
    plot_layout(widths = c(1, 2.2))+
    plot_annotation(tag_levels = 'A')
```

According to Schmassmann et al., 2023, low quality cells have been
filtered from GBM data before the data was archived. Hence, we did not
expect to see bubbles that are enriched with low-quality cells.

Nevertheless, we want to remind the reader that scBubbletree can be used
for QC. In fact, we argue that the above visual is simpler and more
informative than the one used by Schmassmann et al., 2023 which suffers
from overplotting (presented as Figure 1-figure supplement 1 C-D; the
quality feature PercentRibosomal is not visualized in the publication).
We have replicated their visual below:

```{r, fig.width=7, fig.height=6}
(ggplot(data = GBM_meta)+
    facet_wrap(facets = ~tissue, nrow = 1)+
    geom_point(aes(x = tSNE1, y = tSNE2, col = PercentMitochondrial), size=0.5)+
    theme_bw()+
    theme(legend.position = "top")+
    guides(colour = guide_legend(override.aes = list(size=2))))/
(ggplot(data = GBM_meta)+
    facet_wrap(facets = ~tissue, nrow = 1)+
    geom_point(aes(x = tSNE1, y = tSNE2, col = NumberDetectedGenes), size=0.5)+
    theme_bw()+
    theme(legend.position = "top")+
    guides(colour = guide_legend(override.aes = list(size=2))))
```


## Other cell features: **cell phase** and **gene expression**

There is no limit to the number of type of cell features that can be
used to annotate the bubbletree. In the next, we show how to 'attach'
summaries of predicted cell phase labels and gene expressions to the bubbles.

### What is the dominant cell phase in the bubbles? {.unlisted .unnumbered}

Using cell phase as categorical cell features, we visualized the relative 
frequency of cells with a cell phase G1, G2M, and S, within the different 
bubbles.

```{r, fig.width=5.5, fig.height=4}
# cell cycle phase
g_p <- get_cat_tiles(btd = btd,
                     f = GBM_meta$CellCyclePhase,
                     round_digits = 1,
                     tile_text_size = 2,
                     integrate_vertical = FALSE)

(btd$tree|g_p$plot)+
  plot_layout(widths = c(1.5, 1))+
  plot_annotation(tag_levels = 'A')
```


According to the heatmap, the dominant cell phases vary from bubble to
bubble. The cells in the bubbles containing immune cells are
predominantly in G1 phase, i.e. >73% of the cells in each of the
bubbles 6, 4, 0, 9, 7, 1, 2 and 3 are in this phase. This makes sense
from a biological point of view, i.e. most immune cells are likely
resting, and in their quiescent state they do not need to proliferate,
thus they remain in the G0/G1 phase until activated.

In contrast to this, tumor cells, are more likely to be found in S and
G2/ M phases due to their constant division. This is exactly what we
observe, i.e. we see higher fraction of S (synthesis phase) phase for
cells in the bubbles containing tumor cell.

The quantitative summaries encoded in panel B makes the visual generated
by scBubbletree more informative than the complementary t-SNE visual
(see below), in which cells (dots) are color coded according to their
cell phases (presented in Schmassmann et al., 2023 as Figure 1-figure
supplement 1 E).

```{r, fig.width=7, fig.height=3.25}
g7 <- ggplot(data = GBM_meta)+
  facet_wrap(facets = ~tissue, nrow = 1)+
  geom_point(aes(x = tSNE1, y = tSNE2, col = CellCyclePhase), size = 0.5)+
  theme_bw()+
  theme(legend.position = "top")+
  guides(colour = guide_legend(override.aes = list(size=2)))+
  scale_color_discrete(name = "tissue")

g7
```


### What is the average expression of marker genes in each bubble? {.unlisted .unnumbered}

Next, we visualized the average expression values of 26 marker genes in
each bubble (panel C). This is similar to figure 2B in Schmassmann et
al., 2023. Numeric features, such as gene expressions, can be visualized
with scBubbletree. For this we can use the functions `get_num_tiles` or
`get_num_violins`. To generate panel C we used `get_num_tiles`.

```{r, fig.width=9, fig.height=4}
# gene expression
g_e <- get_num_tiles(btd = btd,
                     fs = GBM_exp,
                     summary_function = "mean",
                     round_digits = 1,
                     tile_text_size = 2)

# gene expression
g_ce <- (get_num_cell_tiles(btd = btd, f = GBM_exp[,1], feature_name = "CD68"))$plot|
    (get_num_cell_tiles(btd = btd, f = GBM_exp[,2], feature_name = "TMEM119"))$plot|
    (get_num_cell_tiles(btd = btd, f = GBM_exp[,18], feature_name = "FCGR3A"))$plot|
    (get_num_cell_tiles(btd = btd, f = GBM_exp[,15], feature = "CD8A"))$plot


(btd$tree|g_e$plot)+
  plot_layout(widths = c(1, 3))+
  plot_annotation(tag_levels = 'A')
```

We can evaluate heatmap B to double-check whether the cell type
predictions are consistent with the gene expression of cell type
characteristic markers.

Here are few examples of this analysis:

-   CD14 is a marker of monocytes. CD14 has high average expression in
    cells from bubble 0 ($\approx$ 1.2). We know from the cell type
    annotation visual shown earlier that bubble 0 is enriched with
    monocytes.
-   NCAM1 is a marker of different tumors. NCAM1 has high average
    expression in cells from the tumor cell enriched bubbles 5
    ($\approx$ 1.7) and 8 ($\approx$ 1.9).


### What is the expression of individual cells? {.unlisted .unnumbered}

To visualize numeric features of individual cells we used the function 
`get_num_cell_tiles`, which visualizes numeric attributes of individual 
cells in each bubble using heatmaps, with the cells ordered by the magnitude 
of their numeric attributes. Lets do this for 3 marker genes: CD14, NCAM1 and
CD8A. We see comparable results as in the heatmap generated by `get_num_tiles`.

```{r, fig.width=9, fig.height=4}
# gene expression
g_cd14 <- get_num_cell_tiles(btd = btd,
                          f = GBM_exp[, c("CD14")],
                          feature_name = "CD14")

g_ncam1 <- get_num_cell_tiles(btd = btd,
                          f = GBM_exp[, c("NCAM1")],
                          feature_name = "NCAM1")

g_cd8a <- get_num_cell_tiles(btd = btd,
                          f = GBM_exp[, c("CD8A")],
                          feature_name = "CD8A")


(btd$tree|g_cd14$plot|g_ncam1$plot|g_cd8a$plot)+
  plot_layout(widths = c(1, 1, 1, 1))+
  plot_annotation(tag_levels = 'A')
```


# Summary

`r Biocpkg("scBubbletree")` promotes simple and transparent visual
exploration of scRNA-seq. It is **not a black-box approach** and the
user is encouraged to explore the data with different values of $k$ and
$r$ or custom clustering solutions. Attaching cell features to the
bubbletree is necessary for biological interpretation of the individual
bubbles and their relationships which are described by the bubbletree.

# Session Info

```{r, eval=F, echo=F, include=FALSE}
save.image(file = "image_17_august.RData")


dir.create("manuscript_plots")


# SFig12
ggsave(plot = (g1|g2|btd$tree)+patchwork::plot_annotation(tag_levels = 'A'),
       filename = "manuscript_plots/SFig12.pdf",
       device = "pdf",
       width = 9,
       height = 4)


# SFig13
g3_prim <-g3+
    patchwork::plot_layout(widths = c(1,1.6,2.7,0.7))+
    patchwork::plot_annotation(tag_levels = 'A')
g5 <- g5+patchwork::plot_layout(widths = c(1, 3, 3))
g6 <- g6+patchwork::plot_layout(widths = c(1, 0.7, 5.3))
g56 <- (g3_prim/g5/g6)+patchwork::plot_annotation(tag_levels = 'A')

# SFig15
ggsave(plot = g56,
       filename = "manuscript_plots/SFig13.pdf",
       device = "pdf",
       width = 9,
       height = 12)

ggsave(plot = g_ce,
       filename = "manuscript_plots/SFig13.png",
       device = "png",
       width = 5.35,
       height = 3.4,
       dpi = 600)
```

```{r}
sessionInfo()
```
